%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Trim Size: 9.75in x 6.5in
%% Text Area: 8in (include Runningheads) x 5in
%% ws-ijhr.tex   :  9-5-2005 
%% Tex file to use with ws-ijhr.cls written in Latex2E.
%% The content, structure, format and layout of this style file is the
%% property of World Scientific Publishing Co. Pte. Ltd.
%% Copyright 1995, 2003 by World Scientific Publishing Co.
%% All rights are reserved.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%

%%%%%%%%%%%%% FOR TEMPLATE OF TYPING OUT THE BIBLIOGRAPHY TEXT ONLY %%%%%%%%
\newcounter{myctr}
\def\myitem{\refstepcounter{myctr}\bibfont\parindent0pt\hangindent13pt\themyctr.\enskip}
\def\myhead#1{\vskip10pt\noindent{\bibfont #1:}\vskip4pt}
%%%%%%%%%%%%% FOR TEMPLATE OF TYPING OUT THE BIBLIOGRAPHY TEXT ONLY %%%%%%%%

\documentclass{ws-ijhr}

\hyphenation{op-tical net-works semi-conduc-tor}

\usepackage{graphicx}
\usepackage{multicol}
\usepackage{multirow}
\usepackage[bookmarks=true]{hyperref}
\usepackage{amssymb,amsmath}
\usepackage{subfig}
\usepackage{bbding}

\newcommand{\eq}{Eq.~}
\newcommand{\fig}{Fig.~}
\newcommand{\tab}{Tab.~}
\newcommand{\sect}{Sec.~}

\newcommand{\re}{R}
\newcommand{\rf}{R}
\newcommand{\rl}{L}
\newcommand{\om}{O}
\newcommand{\cm}{M}
\newcommand{\fm}{F}
\newcommand{\hc}{C}
\newcommand{\qd}{Q}
\newcommand{\gpm}{T}
\newcommand{\coll}{W}
\newcommand{\pdf}{\mathbf{pdf}}

\newcommand{\argmax}[1]{\underset{#1}{\operatorname{argmax}}\medspace}

\begin{document}

\markboth{Insert Authors' Names here}{Insert Paper's Title here}

%%%%%%%%%%%%%%%%%%%%% Publisher's Area please ignore %%%%%%%%%%%%%%%
%
\catchline{}{}{}{}{}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{INSTRUCTIONS FOR TYPESETTING MANUSCRIPTS\\
USING COMPUTER SOFTWARE\footnote{For the title, try not to 
use more than 3 lines. Typeset the title in 10~pt 
Times roman, uppercase and boldface.} }

\author{FIRST AUTHOR\footnote{Typeset names in 8~pt roman,
uppercase. Use the footnote to indicate the 
present or permanent address of the author.}}

\address{University Department, University Name, Address\\
City, State ZIP/Zone,
Country\footnote{State completely without abbreviations, the
affiliation and mailing address, including country. Typeset in 8~pt
Times italic.}\\
first\_author@university.edu}

\author{SECOND AUTHOR}

\address{Group, Laboratory, Address\\
City, State ZIP/Zone, Country\\
second\_author@group.com}

\maketitle

\begin{history}
\received{Day Month Year} %
\revised{Day Month Year}  %
\accepted{Day Month Year} %
%\comby{(xxxxxxxxxx)}
\end{history}

\begin{abstract}
\input{abstract}
\end{abstract}

\keywords{Deep learning; generative-evaluative learning; grasping.}

\section{Introduction}

\input{introduction}

\section{Background and Related Work}

\input{related}

\section{The Simulated Grasp Data Set}
\label{section:simulation}
\input{simulation}

\section{The Generative Evaluative Architecture} \label{section:evaluative}
%In this section we describe how the evaluative models are trained and how we perform gradient descent and stochastic simulated annealing to attempt to improve grasps using the evaluative model.
\input{evaluative.tex}


\section{Simulation Analysis}
\label{section:simulationAnalysis}
\input{simulationanalysis}

\section{Extended Simulation Analysis}
\label{section:extendedSimulationAnalysis}
\input{extendedanalysis}

\section*{Acknowledgements}

The authors gratefully acknowledge funding from the European Commission Funded project, PaCMan FP7-IST-600918.

\appendix

\section{Data Efficient Learning of a Generative Grasp Model from Demonstration}

%Describe, in new words, the method from IJRR.
\input{generative} \label{section:generative}

\section{Improved Generative Learning}

%Describe, in new words, the method from IJRR.
\input{generative_improved} \label{section:generative_new}

\section*{References}

%%PLS. NOTE TEMPLATE HERE SHOWN FOR DIFFERENT STYLES FOR 
%%TEXT IN JOURNALS, BOOKS, REVIEW VOLUME AND PROCS. ETC.
%%AT ACTUAL WORK PLS. TYPE WITHOUT THE \myhead COMMAND. 
%%YOU CAN FOLLOW MY EXAMPLE FOR THE COMMAND OF 
%%\thebibliography AFTER THE \end{document} COMMAND.

\vspace*{-5pt}   %ONLY NECESSARY

\myhead{Journal paper}

%1.
\myitem G. Capi, Y. Nasu, L. Barolli, K. Mitobe and K. Takeda,  
Application of genetic algorithms for biped robot gait synthesis 
optimization during walking and going up stairs, 
{\it Advanced Robotics} {\bf 15}(6) (2001) 675--694.

\myhead{Authored book}

%2.
\myitem U. Nehmzow, {\it Mobile Robotics: A Practical 
Introduction}, 2nd edn. (Springer-Verlag, New York, 2003), pp.~25--27.
  
\myhead{Edited book}

%3.
\myitem G. A. Carpenter and S. Grossberg (eds.),  
{\it Neural Networks for Vision and Image Processing} 
(MIT Press, Cambridge, Massachusetts, 1992), pp.~45--60.  

\myhead{Review volume}

%4.
\myitem M. H. Chignell and P. A. Hancock, Horn clause 
representations in human-machine systems with adaptive control, 
in {\it Trends in Ergonomics/Human Factors III}, 
ed.~W. Karwowski (Elsevier, Amsterdam, 1986), p.~76.  

\myhead{Series book}

%5.
\myitem R. M. H. Cheng and R. Rajagopalan, Binary-camera vision  
for guidance control of the automated guided vehicle, in 
{\it Recent Trends in Mobile Robots}, 
Series in Robotics and Automated Systems, Vol.~11 
(World Scientific, New Jersey, 1994), p.~83.

\myhead{Proceedings}

%6.
\myitem A. Dasgupta and Y. Nakamura, Making feasible walking 
motion of humanoid robots from human motion capture data, in 
{\it IEEE Int. Conf. Robotics and Automation (ICRA)} 
(IEEE Press, Detroit, USA, 1999), pp. 1044--1049.
\eject

%FIRST AUTHOR
%\vspace*{13pt}

\vfill\eject

\end{document}

%%BELOW HERE ARE THE SAME BIBLIOGRAPHY TEXT AS ABOVE.
%%PLS. USE THIS COMMAND FOR ACTUAL WORK.
\begin{thebibliography}{0}

\bibitem{1.} G. Capi, Y. Nasu, L. Barolli, K. Mitobe and K. Takeda, 
Application of genetic algorithms for biped robot gait synthesis 
optimization during walking and going up stairs, 
{\it Advanced Robotics} {\bf 15}(6), 675--694 (2001).

\bibitem{2.} U. Nehmzow, {\it Mobile Robotics: A Practical 
Introduction}, 2nd edn. (Springer-Verlag, New York, 2003), pp.~25--27.
  
\bibitem{3.} G. A. Carpenter and S. Grossberg (eds.),  
{\it Neural Networks for Vision and Image Processing} 
(MIT Press, Cambridge, Massachusetts, 1992), pp.~45--60.  

\bibitem{4.} M. H. Chignell and P.A. Hancock, Horn clause 
representations in human-machine systems with adaptive control, 
in {\it Trends in Ergonomics/Human Factors III}, 
ed.~W. Karwowski (Elsevier, Amsterdam, 1986), p.~76.  

\bibitem{5.} R. M. H. Cheng and R. Rajagopalan, Binary-camera vision  
for guidance control of the automated guided vehicle, in 
{\it Recent Trends in Mobile Robots}, 
Series in Robotics and Automated Systems, Vol.~11 
(World Scientific, New Jersey, 1994), p.~83.

\bibitem{6.} A. Dasgupta and Y. Nakamura, Making feasible walking 
motion of humanoid robots from human motion capture data, in 
{\it IEEE Int. Conf. Robotics and Automation (ICRA)} 
(IEEE Press, Detroit, USA, 1999), pp. 1044-1049.

\end{thebibliography}

\end{document}

